Computing Entropies With Nested Sampling

### 2017-05-19 paper/ms.tex
Slight writing

Consider the basic problem of inferring a quantity $\mu$ from
100 observations $\d = \{d_1, ..., d_{100}\}$ whose
probability distribution (conditional on $\mu$) is
\begin{align}
p(d_i | \mu) &\sim \textnormal{Normal}(\mu, 1).
\end{align}
If the prior for $\mu$ is Normal$(0, 10^2)$, then the posterior is
\begin{align}
\mu | \d &\sim \textnormal{Normal}\left(
                                       \frac{1}{100}\sum_{i=1}^{100} d_i,
                                       \left[\frac{10}{\sqrt{10001}}\right]^2
                                       \right).
\end{align}
The true value of $H_{\d}$, calculated analytically, is $146.499$.

The result was
\begin{align}
H_{\d} &= 928.80 \pm 0.38.
\end{align}
The log-volume of a 100-dimensional ball of radius $10^{-3}$ is
-782.017. Therefore, the measured differential en
\section{Example 2: Measuring the period of an oscillating signal}

>>>>

This example demonstrates how the algorithm may be used to determine the
entropy for a quantity whose distribution can only be sampled.
Consider the basic statistics problem of inferring a quantity $\mu$ from
100 observations $\d = \{d_1, ..., d_{100}\}$ whose
probability distribution (conditional on $\mu$) is
\begin{align}
p(d_i | \mu) &\sim \textnormal{Normal}(\mu, 1).
\end{align}
If the prior for $\mu$ is Normal$(0, 10^2)$, then the posterior is
\begin{align}
\mu | \d &\sim \textnormal{Normal}\left(
                                       \frac{1}{100}\sum_{i=1}^{100} d_i,
                                       \left[\frac{10}{\sqrt{10001}}\right]^2
                                       \right).
\end{align}
The true value of the differential entropy $h_{\d}$ is available analytically
in this case, and its value is $146.499$. However, in most situations, the
entropy of a marginal distribution is not available in closed form.

From the algorithm, the expected log-probability was
\begin{align}
?_{\d} &= 928.80 \pm 0.38.
\end{align}
The log-volume of a 100-dimensional ball of radius $10^{-3}$ is
-782.017. Therefore, the measured differential entropy was

\section{Example 2: Measuring the period of an oscillating signal}
